---
title: "Assignment 3"
output: html_document
---

#Question 1

####Death Rate
```{r}
qx_d <- c()
qx_d[55:57] <- c(0.001046, 0.001199, 0.001375)
px_d <- 1-qx_d
```

Different interest rates 
```{r}
i <- 0.06
c <- 0.0192308
IER <- 0.08
RDR <- 0.12
```

####Expected Annuity Payments on Valuation Basis at EOY
```{r}
R.EOY <- rep(0,3)
for(t in 1:3){
  R.EOY[t] <- 15000*(1+c)^(t-1) * prod(px_d[55:(55+t-1)])
}
R.EOY
```

####Expected Expenses at EOY
```{r}
E.EOY <- rep(0,3)
E0 <- 100 + 40250*0.015
f <- 0.05
for(t in 1:3){
  E.EOY[t] <- 10*(1+f)^(t-1) * prod(px_d[55:(55+t-1)])
}
E.EOY
```

####Expected Policy Value, Interest and Transfer at IER at EOY
The policy value in this case at the end of year t is $$_tV=Ra_{{55+t}:{\overline{n-t}|}}$$
```{r}
V.BOY <- rep(0,3)
V.EOY <- rep(0,3)
I.EOY <- rep(0,3)
T.EOY <- rep(0,3)

V.EOY[1] <- (15000*(1+c)/(1+i) *px_d[56] + 15000*(1+c)^2/(1+i)^2 *px_d[56]*px_d[57])*px_d[55]
V.EOY[2] <- (15000*(1+c)^2/(1+i) *px_d[57])*px_d[55]*px_d[56]

V.BOY[1] <- (15000/(1+i) *prod(px_d[55:55]) + 15000*(1+c)/(1+i)^2 *prod(px_d[55:56]) + 15000*(1+c)^2/(1+i)^3 *prod(px_d[55:57])) - 40250
I.EOY[1] <- (40250-E0)*IER
T.EOY[1] <- 40250 - E0 - R.EOY[1] - E.EOY[1] + I.EOY[1] - V.EOY[1]
for(t in 2:3){
  V.BOY[t] <- V.EOY[t-1]
  I.EOY[t] <- V.BOY[t]*IER
  T.EOY[t] <- V.BOY[t] + I.EOY[t] - E.EOY[t] - R.EOY[t] - V.EOY[t]
}
I.EOY
V.EOY
```

##(a)

###(i)
The profit signature is hence the vector of Transfers at EOY
```{r}
T.EOY
```

###(ii)
The expected NPV of profits is just the EPV of profit signature
```{r}
EPV.T_IER <- sum(T.EOY/(1+IER)^(1:3))
EPV.T_IER
```

Under the risk discount rate, the EPV of profits is
```{r}
EPV.T_RDR <- sum(T.EOY/(1+RDR)^(1:3))
EPV.T_RDR
```

Hence the profit margin is
```{r}
EPV.T_RDR/40250
```

##(b)
The IRR can be calculated by finding the root of $NPV(Transfers)=0$
```{r}
NPV <- function(yield){
  sum(T.EOY/(1+yield)^(1:3))
}
IRR <- uniroot(NPV, interval = c(0,1))
IRR
```

Hence, the IRR is 50.29%. The reason of a high IRR in this case is that the EPV of the 3-year repayments is greater than its purchase price 40250.
```{r}
sum(R.EOY/(1+i)^(1:3))
```

#Question 2
####Multiple Decrement Table
```{r}
x <- c(30:40)
qx_d <- c(0.00043, 0.00042, 0.00041, 0.00040, 0.00041, 0.00042, 0.00043, 0.00045, 0.00049, 0.00053)
qx_w <- c(0.25, 0.2, 0.175, rep(0.15,6), 1)

aqx_d <- qx_d * (1-0.5*qx_w)
aqx_w <- qx_w * (1-0.5*qx_d)

al <- rep(0,11)
ad_d <- rep(0,11)
ad_w <- rep(0,11)
al[1] <- 100000
ad_d[1] <- al[1]*aqx_d[1]
ad_w[1] <- al[1]*aqx_w[1]
for(t in 2:11){
  al[t] <- al[t-1]-ad_d[t-1]-ad_w[t-1]
  ad_d[t] <- al[t]*aqx_d[t]
  ad_w[t] <- al[t]*aqx_w[t]
}
```

####Unit Fund
For an in-force policy
```{r}
P.BOY <- c()
P.BOY[1] <- 5000*(1-0.45)*(1-0.005)
P.BOY[2:10] <- 5000*(1-0.01)*(1-0.005)

VoU.EOY <- c()
VoU.EOY[1] <- P.BOY[1]*(1+0.1)*(1-0.003)
for (t in 2:10){
  VoU.EOY[t] <- (VoU.EOY[t-1]+P.BOY[t])*(1+0.1)*(1-0.003)
}
```

Expected amounts per initial policy
```{r}
EP.BOY <- c()
EVoU.EOY <- c()
for(t in 1:10){
  EP.BOY[t] <- P.BOY[t] * al[t]/al[1]
  EVoU.EOY[t] <- VoU.EOY[t] * al[t+1]/al[1]
}

EI_u.EOY <- c()
EI_u.EOY[1] <- EP.BOY[1]*0.1
for(t in 2:10){
  EI_u.EOY[t] <- (EVoU.EOY[t-1]+EP.BOY[t])*0.1
}
```

Transfers to non-unit fund
```{r}
T_u.EOY <- c()
for(t in 2:10){
  T_u.EOY[1] <- EP.BOY[1]+EI_u.EOY[1]-EVoU.EOY[1]
  T_u.EOY[t] <- EVoU.EOY[t-1]+EP.BOY[t]+EI_u.EOY[t]-EVoU.EOY[t]
}
```

####Non-Unit Fund
For an in-force policy
```{r}
PBF.BOY <- 5000*c(0.45, rep(0.01,9))

BSM.BOY <- 0.005*5000*(1-c(0.45, rep(0.01,9)))

E.BOY <- c(5000*0.45, rep(0,9)) + 58*(1+0.2)^(0:9)

DSB.EOY <- VoU.EOY
```

Expected amounts per initial policy
```{r}
EPBF.BOY <- c()
EBSM.BOY <- c()
EE.BOY <- c()
EDB.EOY <- c()
ESB.EOY <- c()
for(t in 1:10){
  EPBF.BOY[t] <- PBF.BOY[t] * al[t]/al[1]
  EBSM.BOY[t] <- BSM.BOY[t] * al[t]/al[1]
  EE.BOY[t] <- E.BOY[t] * al[t]/al[1]
  EDB.EOY[t] <- DSB.EOY[t] * ad_d[t]/al[1]
  ESB.EOY[t] <- DSB.EOY[t] * ad_w[t]/al[1]
}

EI_nu.EOY <- (EPBF.BOY+EBSM.BOY-EE.BOY)*0.08

T_nu.EOY <- EPBF.BOY+EBSM.BOY-EE.BOY+EI_nu.EOY+T_u.EOY-EDB.EOY-ESB.EOY
```

##(a)
The profit signature is
```{r}
T_nu.EOY
```

The EPV of transfers is 
```{r}
sum(T_nu.EOY/(1+0.125)^(1:10))
```

##(b)
We want the transfer from the Unit Fund in year 10 to be higher by 0.7596495.
```{r}
incr <- T_nu.EOY[10]/(1+0.1)
incr
```

So in the Unit Fund we want the policy value at time 9 per inforce policy to increase by
```{r}
incr_u <- incr*al[1]/al[10]
incr_u
```

The new profit signature will be
```{r}
T_nu.EOY_incr <- T_nu.EOY + c(rep(0,8), incr, -T_nu.EOY[10])
T_nu.EOY_incr
```

##(c)
Decreased.

#Question 3